Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-10 ms/main.tex
Fix figure 4

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.45]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_B}.pdf} \\
    ~
    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

>>>>

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection_a}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_b}.pdf} \\
    ~
    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions_c}.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  Figures \textbf{(a)} and \textbf{(b)} describes the expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel \textbf{(a)}, or the transmission bias $T_A-T_B$ on the x-axis of the right panel \textbf{(b)}.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Figure \textbf{(b)} emphasizes an area in which neither phenotype is fixed throughout the simulation, maintaining stochastic coexistence. 
  Figure \textbf{(c)} describes the frequency of cooperators and defactors over time
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  \textbf{(c)} Horizontal transmission rates $T_A = 0.4 < T_B = 0.435$ and cost of cooperation $c=0.02$.
  }
  \label{fig:spatial}
\end{figure}
%TODO: could you revisit figure 4 caption ? I didn't know how to describe the x sign in figure b. DC
